Sex and Power: sexual dimorphism in trait variability and its eco-evolutionary and statistical implications

### 2020-04-30 scripts/MouseSexDiffApril20_2020.Rmd
Just trying to clean up a bit

```{r packages}
library(readr)
library(dplyr)
library(metafor)
library(devtools)
library(purrr)
library(tidyverse)
library(tidyr)
library(tibble)
library(kableExtra)
library(robumeta)
library(ggpubr)
library(ggplot2)
library(here)
# additional packages for intergating male / female symbols in plot 4
library(png)
library(grid)
```

## Functions 
for preparing the data for meta analyses

### 1) Subsetting data
Create function for sub-setting the data to choose only one data point per individual per trait: "data_subset_parameterid_individual_by_age"

@@

### 2) "Population statistics"
Create function called: "calculate_population_stats"
This function groups animals from the same strain and same insitiution together. This is done for each trait seoarately, and only for traits that have been measured in both sexes. Any group containing fewer than 5 individuals is excluded.

```{r PopStatsFunction}
calculate_population_stats <- function(mydata, min_individuals = 5) {
  mydata %>%
    group_by(population, strain_name, production_center, sex) %>%
    summarise(
      trait = parameter_name[1],
      x_bar = mean(data_point),
      x_sd = sd(data_point),
      n_ind = n()
    ) %>%
    ungroup() %>%
    filter(n_ind > min_individuals) %>%
    # Check both sexes present & filter those missing
    group_by(population) %>%
    mutate(
      n_sex = n_distinct(sex)
    ) %>%
    ungroup() %>%
    filter(n_sex == 2) %>%
    select(-n_sex) %>%
    arrange(production_center, strain_name, population, sex)
}
```

@@

This step we have already done and provide a cleaned up file which is less computing intensive and which we have saved in a folder called `export`. However, the cvs is provided in case this is preferred to be attempted, following the steps below: [This code is currently excluded from showing in this html file, but can be viewed and enabled / run in the downloadable .rmd file. However, it requires the .gz file containing the raw data in the "export" folder. Unfortuntaltely, that file can not be provided via github, as is too large (274MB). It is freely accessible, uploaded on zenodo.org (https://zenodo.org/deposit/3759701)

@@

### Supplemental Table 1: "Strains and Center Sample Sizes"
This table summarises the available numbers of male and female mice from each strain and originating institution.

@@

```
### Supplemental Table 3: "Meta-analysis results"

@@

# Metameta_Fig3_female.sig #(Figure 5B left panel)
```
### Supplemental Table 5
SHINICHI
This table provides some of the data plotted in Figures 5 and Figure S2. Here, we provide an overview over meta-analysis results performed on traits that were significantly biased to either sex. This table summarizes findings for both sexes and the respective functional trait groups.

@@

# Supplemental Plots and Tables
### Figure S1 
#### Including lnVR
#### Count data, including lnVR (Fig S1 panel A)

@@

## Heterogeneity Table and Plot
### Supplemental Table 6: "Heterogeneity within groups"
SHINICHI
This table summarizes our findings on heterogeneity due to institutions and mouse strains. These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.

>>>>

```{r packages}
library(readr)
library(dplyr)
library(metafor)
library(devtools)
library(purrr)
library(tidyverse)
library(tidyr)
library(tibble)
library(kableExtra)
library(robumeta)
library(ggpubr)
library(ggplot2)
library(here)
# additional packages for incorporating male / female symbols in plot 4
library(png)
library(grid)
```

## Functions 
Functions needed for preparing the data for meta analyses

### 1) Sub-setting data
Create a function for sub-setting the data to choose only one data point per individual per trait: "data_subset_parameterid_individual_by_age"

@@

### 2) "Population statistics"
Create a function called: "calculate_population_stats"
This function groups animals from the same strain and institution together. This is done for each trait separately, and only for traits that have been measured in both sexes. Any group containing fewer than 5 individuals is excluded.

```{r PopStatsFunction}
calculate_population_stats <- function(mydata, min_individuals = 5) {
  mydata %>%
    group_by(population, strain_name, production_center, sex) %>%
    summarise(
      trait = parameter_name[1],
      x_bar = mean(data_point),
      x_sd = sd(data_point),
      n_ind = n()) %>%
    ungroup() %>%
    filter(n_ind > min_individuals) %>%
    # Check both sexes present & filter those missing
    group_by(population) %>%
    mutate(n_sex = n_distinct(sex)) %>%
    ungroup() %>%
    filter(n_sex == 2) %>%
    select(-n_sex) %>%
    arrange(production_center, strain_name, population, sex)
}
```

@@

We have already done this step and provide a cleaned up file which is less computationally intensive to deal with. The file has been saved in a folder called `export`. However, the `.csv` is provided in case this is preferred and can be imported and processed using following the steps below: [This code is currently excluded from showing in this `.html` file, but can be viewed and enabled / run in the down-loadable .rmd file. However, it requires the .gz file containing the raw data in the "export" folder. Unfortunately, that file can not be provided via Github, as it is too large (274MB). However, it is freely accessible and uploaded to zenodo.org (https://zenodo.org/deposit/3759701)

@@

@@

@@

# Metameta_Fig3_female.sig #(Figure 5B left panel)
```

# Supplemental Plots and Tables

### Supplemental Table S1: "Strains and Center Sample Sizes"
This table summarises the available numbers of male and female mice from each strain and originating institution.

### Supplemental Table S3: "Meta-analysis results"

### Supplemental Table S5: "Sex-biased effect sizes"
SHINICHI
This table provides some of the data plotted in Figures 5 and Figure S2. Here, we provide an overview over meta-analysis results performed on traits that were significantly biased to either sex. This table summarizes findings for both sexes and the respective functional trait groups.

@@

### Supplemental Table S6: "Heterogeneity within groups"
SHINICHI
This table summarizes our findings on heterogeneity due to institutions and mouse strains. These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.

### Figure S1 
#### Including lnVR
#### Count data, including lnVR (Fig S1 panel A)

@@
